### 2018-02-13 Paper_[2018-01-09]_ACMSE/paper.tex
Finalized some more modifications on the ACM paper. Ready to deliver to Dr. Watson for further review.

\section{Introduction}
\label{sec_introduction}

@@

Throughout this section, the same notation will be used as introduced in Section \ref{sec_introduction}. $X \subset \mathbb{R}^d$ is a finite set of points with known response values $f(x)$ for all $x \in X$.

Define a box $b^c = (c,l^c,u^c)$ in $d$ dimensions with center $c \in \mathbb{R}^d$, lower width vector $l^c \in \mathbb{R}^d_+$, and upper width vector $u^c \in \mathbb{R}^d_+$ (where $u^c_i$ refers to the $i$th component of $u^c$). A visual example of a box in two dimensions can be seen in Figure \ref{fig_example_box}. Now, define a componentwise rescaling function $g: \mathbb{R}^d \rightarrow \mathbb{R}^d$ at point $x \in \mathbb{R}^d$ to be
\begin{equation}
  \bigl(g^c(x)\bigr)_r = {k \over 2} \left( 1 + {(x_r - c_r)_- \over l^c_r} - {(x_r - c_r)_+ \over u^c_r} \right)
\end{equation}
where $y_+=\max\{y,0\}$, $y_-=(-y)_+$, $k$ is the order of the box spline as described in Section \ref{sec_box_splines}. Finally, each box spline in a box mesh can be evaluated as $B(g^c(x) \mid A)$ presuming the order of approximation implies $A$. Both box meshes described in the following subsections use box spline basis functions of this form.

@@

    %% Add text to the picture
    \node at (3.25,1.35) {$c$};
    \node at (1.3,1.35) {$l^c_1$};
    \node at (5.1,1.35) {$u^c_1$};
    \node at (2.75,0.55) {$l^c_2$};
    \node at (2.75,1.8) {$u^c_2$};
  \end{tikzpicture}
  \caption{An example box in two dimensions with center $c$, upper widths $u^c_1$, $u^c_2$, and lower widths $l^c_1$, $l^c_2$. Notice that $c$ is not required to be equidistant from opposing sides of the box, that is $u^c_i \not= l^c_i$ is allowed.}
  \label{fig_example_box}
\end{figure}

@@

The first of the three meshes produces a set of boxes around chosen control points and each box has maximal distance between the control point and the nearest side of the box. This centrality property is one mechanism of creating the largest reasonable regions of support for the underlying basis functions. The individual boxes are constructed via the following procedure given a set of control points $C \subseteq X$, $c^{(i)} \in C$,
\begin{enumerate}
  \item Initialize a box $b^{c^{(1)}} \supset X$ with center $c^{(1)}$. \label{step_init}
  \item Identify $c^{(i)}$ over $\bigl\{ j \bigm| j \ne 1$, $B^{c^{(1)}}\bigl( c^{(j)} \bigr) \ne 0 \bigr\}$ that minimizes $\bigl\|c^{(j)}-c^{(1)}\bigr\|_\infty$.  \label{step_closest}
  \item Change the the box $b^{c^{(1)}}$ along the first dimension $r$ such that $\bigl|\bigl|c^{(1)} - c^{(i)}\bigr|\bigr|_\infty = \bigl\vert c^{(1)} - c^{(i)}\bigr\vert_r $, to exclude $c^{(i)}$ from the support of $B^{c^{(1)}}$. \label{step_shrink}
  \item Repeat steps \ref{step_closest} and \ref{step_shrink} until no point in $C$ is in the support of $B^{c^{(1)}}$ (at most $2d$ times, once for each boundary of a box).
\end{enumerate}

@@

While setting the number of boxes equal to the number of points causes the max box mesh to be an interpolant, the generality of the max box mesh approximation can often be improved by bootstrapping the selection of control points. Given a user-selected batch size $s \leq |X|$, start with $s$ well-spaced control points. Next, measure the approximation error at $x \notin C$ and if the error is too large (determined by user), pick $s$ points at which the magnitude of approximation error is largest, add those points to $C$, and recompute the max box mesh. The user is left to decide the batch size $s$ and the error tolerance based on validation performance and computability. Next, the max box mesh is shown to be nearly space filling.

@@

\begin{definition}
A \textit{proper} upper boundary for box $b^x$ at point $y$ occurs when $u^x_r = ||x - y||_\infty$ and $r$ is the first dimension such that $u^x_r = ||x - y||_\infty$, assuming dimensions are deterministically ordered. The same definition applies to lower boundaries.
\end{definition}

\begin{theorem}
A max box mesh composed of $n$ unique control points in $d$ dimensions, $C \subset \mathbb{R}^d$ where all boundaries are proper, is nearly space filling.
\label{theorem_mutual_space_filling}
\end{theorem}
\begin{proof}
Pick an arbitrary point $x \in \mathbb{R}^d$. Now let $c^{(1)}$ be the $c \in C$ that minimizes $|| c - x ||_\infty$, making the nearest box (by max norm) $b^{c^{(1)}}$. Either $x$ is in the support of $b^{c^{(1)}}$ or on the boundary of $b^{c^{(1)}}$ and this is done, or $b^{c^{(1)}}$ has a proper boundary along dimension $r$ with box $b^{c^{(2)}}$ such that $|c^{(2)}_r - x_r| < |c^{(1)}_r - x_r|$. The sequence of bounds $c^{(2)}$, $\ldots$, must be finite for the strict inequality to hold and the last box in this sequence supports $x$. Therefore, the $MBM$ is nearly space filling.
\end{proof}

The max box mesh as proposed is still capable of producing coefficients of 0 for $x \in \mathbb{R}^d$ placed along the boundary of boxes, however this problem is solved by increasing the upper and lower widths of all boxes by the unit roundoff during computation. For this reason, the max box mesh remains a viable strategy for computed approximations. Given a maximum of $c$ control points in $d$ dimensions with $n$ points, the computational complexities are: $\mathcal{O}(c^2 d)$ for computing boxes, $\mathcal{O}(c d^2 + d^3)$ for a least squares fit, and $\mathcal{O}(n / s)$ for bootstrapping (which is multiplicative over the fitting complexities). Evaluating the max box mesh requires $\mathcal{O}(c d)$ computations.

@@

The iterative box mesh ($IBM$) composes box-shaped regions of support over control points that each support strictly one control point just as in the $MBM$, however the mesh is completely space filling by construction and places boxes in a way that reduces apparent error. The boxes are constructed via the following procedure given a finite set of points $X \subset \mathbb{R}^d$,
\begin{enumerate}
\item Add a box with total support around the most central point $x^{(1)} \in X$ to $IBM$ and fit the mesh to all $X$.
\item Add a box centered at $x^{(i)} \notin IBM$ that has the most approximation error, reshaping all boxes in $b^{x^{(j)}} \in IBM$ that contain $x^{(i)}$ by bounding the first dimension $r$ such that $\bigl| x^{(j)}_r - x^{(i)}_r \bigr| = \bigl| \bigl| x^{(j)} - x^{(i)} \bigr| \bigr|_\infty$ and then fit the mesh to all $X$. \label{step_add_box}
\item Repeat Step \ref{step_add_box} until approximation error is below tolerance $t$.
\end{enumerate}

@@

As opposed to the max box mesh, the bootstrapping procedure is built into the iterative box mesh. The user is left to decide the most appropriate error tolerance, however a decision mechanism and analysis is presented in Section \ref{sec_performance_analysis}. Next, it is shown that the $IBM$ is space filling.

\begin{definition}
A \textit{mutual} boundary between boxes $b^x$ and $b^y$ is when there exists an $r$ such that $u^x_r = l^y_r$ or $l^x_r = u^y_r$.
\end{definition}

\begin{theorem} An iterative box mesh composed of $n$ unique control points in $d$ dimensions, $C \subset \mathbb{R}^d$, is space filling. \end{theorem}
\begin{proof}
The first box added to an $IBM$ is space filling by construction. Assume that an $IBM$ composed of $n$ boxes is space filling and a new box centered at $x \in \mathbb{R}^d$ is added. Consider a point $y \in \mathbb{R}^d$. Every box $b^{x^{(i)}}$ that supported $y$ before the addition of $b^x$ and was reshaped along dimension $r \in [1,d]$ has a mutual boundary with $b^x$ by construction. Now either $\bigl| x_r - x^{(i)}_r \bigr| \geq \bigl| y_r - x^{(i)}_r \bigr|$ and $b^{x^{(i)}}$ still supports $y$, or $\bigl| x_r - x^{(i)}_r \bigr| < \bigl| y_r - x^{(i)}_r \bigr|$ and $b^x$ supports $y$. Therefore, the $IBM$ composed of $n+1$ boxes is still space filling.
\end{proof}

@@

The final of the three meshes utilizes $\ell2$ norm distances to define boundaries rather than max norm distances. A well-studied technique for classification and approximation is the nearest neighbor algorithm \cite{cover1967nearest}. The convex region surrounding a central control point in which all points are closer to that center than any other control point is also called the Voronoi cell \cite{dirichlet1850reduction}. The Voronoi mesh ($VM$) utilizes Voronoi cells to define support via a generic basis function $v: \mathbb{R}^d \rightarrow \mathbb{R}$ with

\begin{equation}
v^c(z) = \left(1 - \frac{||z - c||_2}{2 \ dist(z - c \mid c)} \right)_+
\label{eq_voronoi_basis}
\end{equation}

where $c \in \mathbb{R}^d$ is the center of the Voronoi cell, $z \in \mathbb{R}^d$ is an interpolation point, and $dist(\ \cdot \mid c)$ is the distance between $c$ and the nearest boundary of the cell along the vector $\cdot\ $. While all basis functions $v^c(c) = 1$, the $2$ in the denominator causes all basis functions to go linearly to $0$ at the boundary of the twice-expanded Voronoi cell. Note that this basis function is $C^0$ because the boundaries of the Voronoi cell are $C^0$. In the case that there is no boundary along the vector $x-c$, the basis function value is always $1$.

While the cost of computing all Voronoi cells for any given set of points grows exponentially \cite{dutour2009complexity}, the calculation of $dist$ is linear with respect to the number of control points and dimensions. Given any center $c^{(1)} \in \mathbb{R}^d$, set of control points $C \subset \mathbb{R}^d$, and interpolation point $z \in \mathbb{R}^d$, $dist\bigl((z-c^{(1)}) \mid c^{(1)}\bigr)$ is the solution to
\begin{equation}
  \max_{\{c \in C\}\backslash c^{(1)}} \frac{|z|}{2} \ \frac{z \cdot \bigl(c - c^{(1)}\bigr) - c^{(1)} \cdot \bigl(c - c^{(1)}\bigr)}{c \cdot \bigl(c - c^{(1)}\bigr) - c^{(1)} \cdot \bigl(c - c^{(1)}\bigr)}.
\end{equation}

The parameters of the $VM$ can now be computed exactly as for the $MBM$ and $IBM$. The vornonoi mesh is used to generate a $|X| \times |C|$ matrix $M$ of basis function evaluations at all points in $X$. Now the set of coefficients for each basis function is the solution to the least squares problem $\min_P \bigl\| M \ P - f(X) \bigr\|_2$. When $X = C$, $M$ is the identity making the mesh an interpolant. Bootstrapping can be performed with an identical procedure to that of the $IBM$.
\begin{enumerate}
\item Pick the most central point $x^{(1)} \in X$ to be the first control point in $VM$ and fit the mesh to all $X$.
\item Add a control point $x^{(i)} \notin VM$ that has the most approximation error and then fit the mesh to all $X$. \label{step_add_control}
\item Repeat Step \ref{step_add_control} until approximation error is below tolerance $t$.
\end{enumerate}

Any $VM$ is na\"{\i}vely space filling, since any possible interpolation point will have a nearest neighbor control point when the set of control points is nonempty.

\begin{theorem}
  A Voronoi mesh composed of $n$ unique control points in $d$ dimensions, $C \subset \mathbb{R}^d$, is space filling.
\end{theorem}
\begin{proof}
  Consider interpolating at point $z$. Let $c^{(1)}$ be the $c \in C$ that minimizes $||z-c||_2$. Now, $z$ must be in the support of the basis function $v^{c^{(1)}}$. Therefore the Voronoi mesh is space filling.
\end{proof}

The computational complexity of evaluating a parameterized Voronoi mesh with $c$ control points is $\mathcal{O}(c^2 d)$. Bootrsapping the generation of a Voronoi mesh requres $\mathcal{O}(c^2 n d)$ computations for a maximum number of basis functions $c$ determined by the error threshold.

@@

\section{Data and Analysis}
In order to evaluate the proposed interpolation and approximation techniques, this paper utilizes three data sets of varying dimension and application. In the following subsections the sources and targets of each data set are described, as well as challenges and limitations related to doing interpolation and approximation on these data sets. The distributions of response values being modeled can be seen in Figure \ref{fig_response_hists}. The preprocessing and approximation processes are described in Section \ref{sec_performance_analysis}.

@@

\subsubsection{High Performance Computing I/O}
$$N = 532, D = 4$$
The first of three data sets is a four-dimensional dataset produced by executing the IOzone benchmark from \cite{iozone} on a homogeneous cluster of computers. The system performance data was collected by executing IOzone 40 times for each of a select set of system configurations. A single IOzone execution reports the max I/O file-read throughput seen. The 40 executions for each system configuration are converted to their mean, which is capable of being modeled by each of the multivariate approximation techniques presented in Section \ref{sec_mesh_construction}. The four dimensions being modelled to predict throughput mean are file size, record size, thread count, frequency.

@@

The forest fire data set provided by \cite{cortez2007data}, describes the area of Montesinho park burned on specific days and months of the year in terms of the environmental conditions. The twelve dimensions being used to model burn area are the $x$ and $y$ spatial coordinates of burns in the park, month and day of year, the FFMC, DMC, DC, and ISI indices (see source for details), the temperature in celcius, relative humidity, wind speed, and outdoor rain. The original analysis of this data set demonstrated it to be difficult to model, likely due to the skew in response values.

@@

The final data set for evaluation is derived from a speech monitoring study with the intent to automatically estimate Parkinson's disease symptom development in parkinsons patients from \cite{tsanas2010accurate}. Particularly, a time-consuming clincal evaluation measure referred to as the UPDRS score. The total UPDRS score given by a clinical evaluation is estimated through 16 real numbers generated from biomedical voice measures of in-home sound recordings.

@@

\begin{figure*}[htb]
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.95\textwidth,height=9.5cm]{all-performance.pdf}};
    \node[below=of img, node distance=0cm, yshift=1cm] {Relative Error Tolerance while Bootstrapping};
    \node[left=of img, node distance=0cm, rotate=90, anchor=center,yshift=-0.7cm] {Signed Relative Error};
  \end{tikzpicture}
  \caption{The performance of all three techniques with varied relative error tolerance for the bootstrapping parameter. The columns are for Max Box Mesh, Iterative Box Mesh, and Voronoi Mesh, respectively. The rows are for HPC I/O, Forest Fire, and Parkinsons respectively. Notice that the techniques exibit counterintuitive behavior on the Parkinsons and Forest Fire data sets, performance increases with increasing error tolerance.}
  \label{fig_all_performance}
\end{figure*}

The performance of the approximation techniques varies considerably across the three evaluation data sets. Relative errors for the most na\"{\i}ve approximators such as nearest neighbor can range $\displaystyle [0, \big(\max_x f(x) - \min_x f(x)\big) / \min_x f(x) ]$ when modeling a nonnegative function $f(x)$ from data. Each of the approximation techniques presented remain within these bounds and all errors are presented in signed relative form $(\hat f(x) - f(x)) / f(x)$. Before the models are constructed all data $X$ values are shifted and scaled to be in the unit cube $[0,1]$, while the response values are taken in their original form. All models are evaluated with a 10-fold cross validation over 80:20 splits of the data.

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    \hline
    \textbf{Data Set} & \textbf{Technique} & \textbf{Tolerance} & \textbf{Average Errror}\\
    \hline
    HPC I/O & MBM & 1.2 & 0.597\\
    Forest Fire & MBM & 1.8 & 3.517\\
    Parkinsons & MBM & 0.6 & 0.114\\
    \hline
    HPC I/O & IBM & 0.4 & 0.419\\
    Forest Fire & IBM & 1.8 & 3.615\\
    Parkinsons & IBM & 1.8 & 0.121\\
    \hline
    HPC I/O & VM & 0.2 & 0.382\\
    Forest Fire & VM & 1.0 & 4.783\\
    Parkinsons & VM & 2.0 & 1.824\\
    \hline
  \end{tabular}
  \caption{The optimial error tolerance bootstrapping parameters for each technique and each data set as well as the average absolute relative errors achieved by that tolerance. Notice that large relative error tolerances occasionally yield even lower evaluation errors, demonstrating the benefits of approximation over interpolation for noisy data sets.
  \vspace{-1cm}}
  \label{tab_optimal_tolerance}
\end{table}

@@

\begin{figure*}[htb]
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.95\textwidth,height=9.5cm]{perf-sample.pdf}};
    \node[below=of img, node distance=0cm, yshift=1cm] {Signed Relative Error in Prediction};
    \node[left=of img, node distance=0cm, rotate=90, anchor=center,yshift=-0.7cm] {Count};
  \end{tikzpicture}
  \caption{A sample of relative errors for all three techniques with optimal selections of error tolerance. The columns are for Max Box Mesh, Iterative Box Mesh, and Voronoi Mesh, respectively. The rows are for HPC I/O, Forest Fire, and Parkinsons respectively. Notice that the Max Box Mesh exibits the least skewed distribution of errors across all three data sets.
    \vspace{-.3cm}}
  \label{fig_perf_sample}
\end{figure*}

The selection of bootstrapping error tolerance also effects the computation time required to fit each of the models to data. Figure \ref{fig_eval_times} presents the time required to construct approximations for each model and each data set with varying $t$. The rapid reducting in computation time required for the forest fire and HPC I/O data sets suggests that large reductions in error can be achieved with relatively few basis functions. The Parkinson's data set however presents a more noisy response, with increasing number of basis functions reducing error much less quickly.

The distributions of errors experienced by each approximation technique when the optimal bootstrapping relative error tolerance is selected can be seen in Figure \ref{fig_perf_sample}. HPC I/O exibits the most normal approximation errors, which suggests that the models are converging on the latent noise of the response for the data set. The worst relative approximation errors are produced by the Voronoi mesh on the forest fire data set. The small magnitude true response values contribute to the larger relative errors, however the $VM$ performances are still unacceptably large.

>>>>

\def\mn#1{\left\Vert #1\right\Vert_\infty} 
\section{Introduction}
\label{sec_introduction}

@@

Throughout this section, the notation will be reused from Section \ref{sec_introduction}. $X \subset \mathbb{R}^d$ is a finite set of points with known response values $f(x)$ for all $x \in X$. Also let $L,U \in \mathbb{R}^d$ define a bounding box for $X$ such that $L < x < U$ for all $x \in X$ (and comparison is componentwise).

Define a box $b^c = (c,l^c,u^c)$ in $d$ dimensions with anchor $c \in \mathbb{R}^d$, lower width vector $l^c \in \mathbb{R}^d_+$, and upper width vector $u^c \in \mathbb{R}^d_+$ (where $u^c_i$ refers to the $i$th component of $u^c$). A visual example of a box in two dimensions can be seen in Figure \ref{fig_example_box}. Now, define a componentwise rescaling function $g: \mathbb{R}^d \rightarrow \mathbb{R}^d$ at point $x \in \mathbb{R}^d$ to be
\begin{equation}
  \bigl(g^c(x)\bigr)_r = {k \over 2} \left( 1 - {(x_r - c_r)_- \over l^c_r} + {(x_r - c_r)_+ \over u^c_r} \right),
\end{equation}
where $y_+=\max\{y,0\}$, $y_-=(-y)_+$, $k$ is the order of the box spline as described in Section \ref{sec_box_splines}. Finally, each box spline in a box mesh can be evaluated as $B^c(x)$, where $B^c(x) = B(g^c(x) \mid A)$ presuming the order of approximation implies $A$. Both box meshes described in the following subsections use box spline basis functions of this form.

@@

    %% Add text to the picture
    \node at (3.25,1.35) {$c$};
    \node at (1.3,1.35) {$l^c_1$};
    \node at (5.1,1.35) {$u^c_1$};
    \node at (2.75,0.55) {$l^c_2$};
    \node at (2.75,1.8) {$u^c_2$};
  \end{tikzpicture}
  \caption{An example box in two dimensions with anchor $c$, upper widths $u^c_1$, $u^c_2$, and lower widths $l^c_1$, $l^c_2$. Notice that $c$ is not required to be equidistant from opposing sides of the box, that is $u^c_i \not= l^c_i$ is allowed.}
  \label{fig_example_box}
\end{figure}

@@

The first of the three meshes produces a set of boxes around chosen control points and each box has maximal distance between the control point and the nearest side of the box. This centrality property is one mechanism for creating the largest reasonable regions of support for the underlying basis functions. The individual boxes are constructed via the following procedure given a set of control points $C \subseteq X$, $c^{(i)} \in C$,
\begin{enumerate}
  \item Initialize a box $b^{c^{(1)}} = \bigl(c^{(1)}, (c^{(1)} - L), (U - c^{(1)})\bigr)$. \label{step_init}
  \item Identify $c^{(i)}$ over $\bigl\{ j \bigm| j \ne 1$, $B^{c^{(1)}}\bigl( c^{(j)} \bigr) \ne 0 \bigr\}$ that minimizes $\bigl\|c^{(j)}-c^{(1)}\bigr\|_\infty$.  \label{step_closest}
  \item Change the the box $b^{c^{(1)}}$ along the first dimension $r$ such that $\bigl|\bigl|c^{(1)} - c^{(i)}\bigr|\bigr|_\infty = \bigl\vert c^{(1)} - c^{(i)}\bigr\vert_r $, to exclude $c^{(i)}$ from the support of $B^{c^{(1)}}$. \label{step_shrink}
  \item Repeat steps \ref{step_closest} and \ref{step_shrink} until no point in $C$ is in the support of $B^{c^{(1)}}$ (at most $2d$ times, once for each boundary of a box).
\end{enumerate}

@@

While setting the number of boxes equal to the number of points causes the max box mesh to be an interpolant, the generality of the max box mesh approximation can often be improved by bootstrapping the selection of control points. Given a user-selected batch size $s \leq |X|$, start with $s$ well-spaced control points. Next, measure the approximation error at $x \notin C$ and if the error is too large (determined by user), pick $s$ points at which the magnitude of approximation error is largest, add those points to $C$, and recompute the max box mesh. The user is left to decide the batch size $s$ and the error tolerance based on validation performance and computability. This work uses a batch size of one.

@@

Throughout all experiments and all repeated trials conducted for this study, all tested interpolation points were covered by at least one box in the $MBM$. However, it is possible for the $MBM$ to not form a covering of $(L,U)$ when there are cyclic boundaries. Consider the following example in three dimensions:
\begin{align*}
  C         &= \bigl\{(0,0,0), (1,0,2/3), (1,1,4/3)\bigr\} \\
  b^{c^{(1)}} &= \bigl( (0,0,0),  \ (*,*,*),  \ (1,*,4/3) \bigr) \\
  b^{c^{(2)}} &= \bigl( (1,0,2/3),\ (1,*,*),  \ (*,1,*)   \bigr) \\
  b^{c^{(3)}} &= \bigl( (1,1,4/3),\ (*,1,4/3),\ (*,*,*)   \bigr)
\end{align*}
Asterisks are used to represent boxes that are not bounded by other boxes along some dimensions. The point $(2,2,-3)$ is not in any of the max boxes defined above. In this case, there is a cycle in box boundaries that looks like $\bigl( b^{c^{(1)}} \bigm\vert_1 b^{c^{(2)}} \bigm\vert_2 b^{c^{(3)}} \bigm\vert_3 b^{c^{(1)}} \bigr)$, where $\bigl( b^x \bigm\vert_r b^y \bigr)$ is used to denote ``$b^x$ is bounded on dimension $r$ by $b^y$''. This example demonstrates that it is geometrically possible for the max box mesh to fail to cover a space, however experiments demonstrate that it is empirically unlikely.

The max box mesh remains a viable strategy for computed approximations. Given a maximum of $c$ control points in $d$ dimensions with $n$ points, the computational complexities are: $\mathcal{O}(c^2 d)$ for computing boxes, $\mathcal{O}(c d^2 + d^3)$ for a least squares fit, and $\mathcal{O}(n / s)$ for bootstrapping (which is multiplicative over the fitting complexities). Evaluating the max box mesh requires $\mathcal{O}(c d)$ computations.

@@

The iterative box mesh ($IBM$) composes box-shaped regions that each contain strictly one control point just as in the $MBM$. However, the mesh is a covering for $(L,U)$ by construction and places boxes in a way that reduces apparent error. The boxes are constructed via the following procedure given a finite set of points $X \subset \mathbb{R}^d$, where $C \subseteq X$ is the (initially empty) set of control points
\begin{enumerate}
\item Add a box that covers $(L,U)$ anchored at the most central point $x^{(1)} \in X$ to $C$ and fit the $IBM$ to all $X$.
\item Add a new box that covers $(L,U)$ anchored at $x^{(i)} \notin C$ such that $x^{(i)} = \max_{x \in X \backslash C} \bigl| \hat f(x) - f(x) \bigr|$, reshaping all boxes $b^{x^{(j)}} \in C$ that contain $x^{(i)}$ by bounding the first dimension $r$ such that $\bigl| x^{(j)}_r - x^{(i)}_r \bigr| = \bigl\| x^{(j)} - x^{(i)} \bigr\|_\infty$ (also reshaping the box $b^{x^{(i)}}$ symmetrically) and then fit the mesh to all $X$. \label{step_add_box}
\item Repeat Step \ref{step_add_box} until approximation error is below tolerance $t$.
\end{enumerate}

@@

As opposed to the max box mesh, the bootstrapping procedure is built into the iterative box mesh. The user is left to decide the most appropriate error tolerance, however a decision mechanism and analysis is presented in Section \ref{sec_performance_analysis}. As mentioned earlier, the iterative box mesh is a covering for $(L,U)$ by construction and this can be proved by an inductive argument.

@@

The final of the three meshes utilizes $\ell2$ norm distances to define boundaries rather than max norm distances. A well-studied technique for classification and approximation is the nearest neighbor algorithm \cite{cover1967nearest}. Nearest neighbor inherently utilizes the convex region $v^{x^{(i)}}$ (Voronoi cell \cite{dirichlet1850reduction}) consisting of all points closer to $x^{(i)}$ than any other point $x^{(j)}$. The Voronoi mesh smooths the nearest neighbor approximation by utilizing the Voronoi cells to define support via a generic basis function $V: \mathbb{R}^d \rightarrow \mathbb{R}_+$ given by

$$ V^{x^{(i)}}(y) = \left(1 - \frac{||y - x^{(i)}||_2}{2 \ d(y - x^{(i)} \mid x^{(i)})} \right)_+, $$
where $x^{(i)}$ is the center of the Voronoi cell, $y \in \mathbb{R}^d$ is an interpolation point, and $d(w \mid x^{(i)})$ is the distance between $x^{(i)}$ and the boundary of the Voronoi cell $v^{x^{(i)}}$ in the direction $w$. $V^{x^{(i)}}\bigl(x^{(j)}\bigr) = 0$ and $V^{x^{(i)}}$ has local support. While all basis functions $V^{x^{(i)}}(x^{(i)}) = 1$, the $2$ in the denominator causes all basis functions to go linearly to $0$ at the boundary of the twice-expanded Voronoi cell. Note that this basis function is $C^0$ because the boundaries of the Voronoi cell are $C^0$. In the case that there is no boundary along the vector $w$, the basis function value is always $1$.

While the cost of computing the exact Voronoi cells for any given set of points grows exponentially \cite{dutour2009complexity}, the calculation of $d$ is linear with respect to the number of control points and dimensions. Given any center $x^{(i)} \in \mathbb{R}^d$, set of control points $C \subseteq X$, and interpolation point $y \in \mathbb{R}^d$, $d\bigl((y-x^{(i)}) \mid x^{(i)}\bigr)$ is the solution to
\begin{equation}
  \max_{\{c \in C\}\backslash x^{(i)}} \frac{\|y\|_2}{2} \ \frac{y \cdot \bigl(c - x^{(i)}\bigr) - x^{(i)} \cdot \bigl(c - x^{(i)}\bigr)}{c \cdot \bigl(c - x^{(i)}\bigr) - x^{(i)} \cdot \bigl(c - x^{(i)}\bigr)}.
\end{equation}

The parameters of the $VM$ can now be computed exactly as for the $MBM$ and $IBM$. The Voronoi mesh is used to generate a $|X| \times |C|$ matrix $M$ of basis function evaluations at all points in $X$. Now the set of coefficients for each basis function is the solution to the least squares problem $\min_P \bigl\| M \ P - f(X) \bigr\|_2$. When $X = C$, $M$ is the identity making the mesh an interpolant. Bootstrapping can be performed with an identical procedure to that of the $IBM$.
\begin{enumerate}
\item Pick the most central point $x^{(1)} \in X$ to be the first control point in $C$ and fit the $VM$ to all $X$.
\item Add a control point $x^{(i)} \notin C$ such that $x^{(i)} = \max_{x \in X \backslash C} \bigl| \hat f(x) - f(x) \bigr|$ and then fit the $VM$ to all $X$. \label{step_add_control}
\item Repeat Step \ref{step_add_control} until approximation error is below tolerance $t$.
\end{enumerate}

Any $VM$ is na\"{\i}vely a covering for $(L,U)$, since any possible interpolation point will have a nearest neighbor control point. The computational complexity of evaluating a parameterized Voronoi mesh with $c$ control points is $\mathcal{O}(c^2 d)$. Bootstrapping the generation of a Voronoi mesh requires $\mathcal{O}(c^2 n d)$ computations for a maximum number of basis functions $c$ determined by the error threshold.

@@

\section{Data and Analysis}
In order to evaluate the proposed interpolation and approximation techniques, this paper utilizes three data sets of varying dimension and application. In the following subsections the sources and targets of each data set are described, as well as challenges and limitations related to interpolating and approximating these data sets. The distributions of response values being modeled can be seen in Figure \ref{fig_response_hists}. The preprocessing and approximation processes are described in Section \ref{sec_performance_analysis}.

@@

\subsubsection{High Performance Computing I/O}
$$N = 532, D = 4$$
The first of three data sets is a four-dimensional data set produced by executing the IOzone benchmark from \cite{iozone} on a homogeneous cluster of computers. The system performance data was collected by executing IOzone 40 times for each of a select set of system configurations. A single IOzone execution reports the max I/O file-read throughput seen. The 40 executions for each system configuration are converted to their mean, which is capable of being modeled by each of the multivariate approximation techniques presented in Section \ref{sec_mesh_construction}. The four dimensions being modeled to predict throughput mean are file size, record size, thread count, and frequency.

@@

The forest fire data set provided by \cite{cortez2007data}, describes the area of Montesinho park burned on specific days and months of the year in terms of the environmental conditions. The twelve dimensions being used to model burn area are the $x$ and $y$ spatial coordinates of burns in the park, month and day of year, the FFMC, DMC, DC, and ISI indices (see source for details), the temperature in Celsius, relative humidity, wind speed, and outdoor rain. The original analysis of this data set demonstrated it to be difficult to model, likely due to the skew in response values.

@@

The final data set for evaluation is derived from a speech monitoring study with the intent to automatically estimate Parkinson's disease symptom development in Parkinson's patients from \cite{tsanas2010accurate}. Particularly, a time-consuming clinical evaluation measure referred to as the UPDRS score. The total UPDRS score given by a clinical evaluation is estimated through 16 real numbers generated from biomedical voice measures of in-home sound recordings.

@@

\begin{figure*}[htb]
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.95\textwidth,height=9.5cm]{all-performance.pdf}};
    \node[below=of img, node distance=0cm, yshift=1cm] {Relative Error Tolerance while Bootstrapping};
    \node[left=of img, node distance=0cm, rotate=90, anchor=center,yshift=-0.7cm] {Signed Relative Error};
  \end{tikzpicture}
  \caption{The performance of all three techniques with varied relative error tolerance for the bootstrapping parameter. The columns are for Max Box Mesh, Iterative Box Mesh, and Voronoi Mesh, respectively. The rows are for HPC I/O, Forest Fire, and Parkinson's respectively. Notice that the techniques exhibit counterintuitive behavior on the Parkinson's and Forest Fire data sets, performance increases with larger error tolerance.}
  \label{fig_all_performance}
\end{figure*}

The performance of the approximation techniques varies considerably across the three evaluation data sets. Relative errors for the most na\"{\i}ve approximators such as nearest neighbor can range $\displaystyle [0, \big(\max_x f(x) - \min_x f(x)\big) / \min_x f(x) ]$ when modeling a nonnegative function $f(x)$ from data. Each of the approximation techniques presented remain within these bounds and all errors are presented in signed relative form $(\hat f(x) - f(x)) / f(x)$. Before the models are constructed all data $X$ values are shifted and scaled to be in the unit cube $[0,1]$, while the response values are taken in their original form. All models are evaluated with $10$ random $80/20$ splits of the data.

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    \hline
    \textbf{Data Set} & \textbf{Technique} & \textbf{Tolerance} & \textbf{Average Error}\\
    \hline
    HPC I/O & MBM & 1.2 & 0.597\\
    Forest Fire & MBM & 1.8 & 3.517\\
    Parkinson's & MBM & 0.6 & 0.114\\
    \hline
    HPC I/O & IBM & 0.4 & 0.419\\
    Forest Fire & IBM & 1.8 & 3.615\\
    Parkinson's & IBM & 1.8 & 0.121\\
    \hline
    HPC I/O & VM & 0.2 & 0.382\\
    Forest Fire & VM & 1.0 & 4.783\\
    Parkinson's & VM & 2.0 & 1.824\\
    \hline
  \end{tabular}
  \caption{The optimal error tolerance bootstrapping parameters for each technique and each data set as well as the average absolute relative errors achieved by that tolerance. Notice that large relative error tolerances occasionally yield even lower evaluation errors, demonstrating the benefits of approximation over interpolation for noisy data sets.
  \vspace{-1cm}}
  \label{tab_optimal_tolerance}
\end{table}

@@

\begin{figure*}[htb]
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.95\textwidth,height=9.5cm]{perf-sample.pdf}};
    \node[below=of img, node distance=0cm, yshift=1cm] {Signed Relative Error in Prediction};
    \node[left=of img, node distance=0cm, rotate=90, anchor=center,yshift=-0.7cm] {Count};
  \end{tikzpicture}
  \caption{A sample of relative errors for all three techniques with optimal selections of error tolerance. The columns are for Max Box Mesh, Iterative Box Mesh, and Voronoi Mesh, respectively. The rows are for HPC I/O, Forest Fire, and Parkinson's respectively. Notice that the Max Box Mesh exibits the least skewed distribution of errors across all three data sets.
    \vspace{-.3cm}}
  \label{fig_perf_sample}
\end{figure*}

The selection of bootstrapping error tolerance also effects the computation time required to fit each of the models to data. Figure \ref{fig_eval_times} presents the time required to construct approximations for each model and each data set with varying $t$. The rapid reduction in computation time required for the forest fire and HPC I/O data sets suggests that large reductions in error can be achieved with relatively few basis functions. The Parkinson's data set however presents a more noisy response, with increasing number of basis functions reducing error much less quickly.

The distributions of errors experienced by each approximation technique when the optimal bootstrapping relative error tolerance is selected can be seen in Figure \ref{fig_perf_sample}. HPC I/O exhibits the most normal approximation errors, which suggests that the models are converging on the random noise of the response for the data set. The worst relative approximation errors are produced by the Voronoi mesh on the forest fire data set. The small magnitude true response values contribute to the larger relative errors. Regardless, the $VM$ errors are unacceptably large.
